Modelling BCG vaccination in the UK

### 2019-05-03 rmds/07-direct-effect-bcg-change.Rmd
reorganised thesis to work with online gitbook
Former-commit-id: 3fd8c59438bc22ef6b09d75159886a79ea855f4e
drop cache
Former-commit-id: 6c4a4897bab98af709a1d386ddb45d420e0605d8

```{r 07-knitr-options, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 320,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center')
```

@@

## Read formated results
## See https://github.com/seabbs/DirectEffBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
read_formated <- function(name) {
  path <- file.path("chapters/direct-eff-bcg-change", paste0(name, ".rds"))

@@

```{r best-fitting-models, messages = FALSE, warnings = FALSE, include = FALSE}
## Combine model summary and fitted models
BestFitTargetedUKBorn <- read_formated("best-targeted-ukborn")
BestFitUniversalUKBorn <- read_formated("best-universal-ukborn")
## Combine model summary and fitted models
BestFitTargetedNonUKBorn <- read_formated("best-targeted-nonukborn")
BestFitUniversalNonUKBorn <- read_formated("best-universal-nonukborn")
```

>>>>

```{r 07-knitr-options, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 320,
                      fig.width = 8, fig.height = 8,
                      out.width = "80%", fig.align = 'center', cache = FALSE)
```

@@

## Read formated results
## See https://github.com/seabbs/DirectEffBCGPolicyChange/blob/master/vignettes/paper.Rmd
## for code required to reproduce 
## Chapter is an edited version of the orginal reproducible document.
##Wordcount: 4410
read_formated <- function(name) {
  path <- file.path("chapters/direct-eff-bcg-change", paste0(name, ".rds"))

@@

```{r best-fitting-models, messages = FALSE, warnings = FALSE,include = FALSE, cache = FALSE}
## Combine model summary and fitted models
BestFitTargetedUKBorn <- read_formated("best-targeted-ukborn")
BestFitUniversalUKBorn <- read_formated("best-universal-ukborn")
## Combine model summary and fitted models
BestFitTargetedNonUKBorn <- read_formated("best-targeted-nonukborn")
BestFitUniversalNonUKBorn <- read_formated("best-universal-nonukborn")
```
